---
title: "hw_2"
author: "Sihyuan Han"
date: "2020/09/09"
output:
  html_document: default
  pdf_document: default
---

```{r}
library(tidyverse)
```


# Implement a fizzbuzz() function

```{r}
fizzbuzz <- function(x){
  if (x%%3 == 0 && x%%5 != 0) {
    return("fizz")
  } else if (x%%3 != 0 && x%%5 == 0) {
    return("buzz")
  } else if (x%%3 == 0 && x%%5 == 0) {
    return("fizzbuzz")
  } else {
    return(x)
  }
}
fizzbuzz(3)
fizzbuzz(5)
fizzbuzz(15)
fizzbuzz(16)
```

* 1-c

```{r}
fizzbuzz <- function(x){
  if (x%%3 == 0 && x%%5 != 0) {
    return("fizz")
  } else if (x%%3 != 0 && x%%5 == 0) {
    return("buzz")
  } else if (x%%3 == 0 && x%%5 == 0) {
    return("fizzbuzz")
  } else {
    return(x)
  }
}
fizzbuzz(3)
fizzbuzz(5)
fizzbuzz(15)
fizzbuzz(2)
```

* 1-e include error checking

```{r, error=TRUE}
fizzbuzz <- function(x){
stopifnot(length(x)==1)
  stopifnot(is.numeric(x))
  if (x%%3 == 0 && x%%5 != 0) {
    return("fizz")
  } else if (x%%3 != 0 && x%%5 == 0) {
    return("buzz")
  } else if (x%%3 == 0 && x%%5 == 0) {
    return("fizzbuzz")
  } else {
    return(x)
  }
}
fizzbuzz("cat")
fizzbuzz(c(1,5))
```

* 1-f completing Roxygen comments in the code chunk

```{r}
#' fizzbuzz #Title
#' fizzbuzz(x%%3 == 0 && x%%5 == 0) # Useage
#' @param x Input a number
#'
#' @return If the input number is divisible by three, five or three and five, or none
#'
#' @examples
#' fizzbuzz(3)
#' fizzbuzz(5)
#' fizzbuzz(15)
#' fizzbuzz(2)
fizzbuzz <- function(x){
stopifnot(length(x)==1)
  stopifnot(is.numeric(x))
  if (x%%3 == 0 && x%%5 != 0) {
    return("fizz")
  } else if (x%%3 != 0 && x%%5 == 0) {
    return("buzz")
  } else if (x%%3 == 0 && x%%5 == 0) {
    return("fizzbuzz")
  } else {
    return(x)
  }
}
```


* 1-g Create a script out of your fizzbuzz() function

```{r}
cat(readr::read_file("fizzbuzz_s.R"))
```
```{r}
source('~/stat_612(R)/Rwk2_hw2/fizzbuzz_s.R')
fizzbuzz_s(35)
fizzbuzz_s(18)
fizzbuzz_s(45)
fizzbuzz_s(-1)
```


## Create a new cut() function

```{r}
show_temp <- function(x){seq(-20,100,by=5)
cut(x, c(-Inf,0,10,20,30,Inf), right = TRUE, labels = c("freezing","cold","cool","warm","hot"))
}
show_temp(31)
show_temp(30)
show_temp(10)
show_temp(-10)
```

* Change the call to cut() to handle < instead of <= in the comparisons

```{r}
show_temp <- function(x){seq(-20,100,by=5)
cut(x, c(-Inf,0,10,20,30,Inf), right = FALSE, labels = c("freezing","cold","cool","warm","hot"))
}
show_temp(31)
show_temp(30)
show_temp(10)
show_temp(-10)
```

* 2-c What is the other chief advantage of the cut() method for this problem?
    + Ans: If there are many values in temp, using cut() can easily define the break instead of writing very long if-else codes


###  Using the Forward Pipe

```{r}
sample(1:10,1000,replace=TRUE) %>%
  mean() %>%
  exp()
```


#### Calculate a proportion

```{r}
rnorm(100,10,9)
a <- rnorm(100,10,9)
a>12
```


##### Logical Comparisons and Subsetting

```{r}
x <- c(TRUE, FALSE, TRUE, TRUE)
y <- c(FALSE, FALSE, TRUE, FALSE)
z <- NA
x & y
x & z
!(x | y)
x | y
y | z
x[y]
y[x]
x[x|y]
```





