---
title: "hw_dplyr_p1p2"
author: "Sihyuan Han"
output:
  pdf_document: default
  html_document: default
  word_document: default
Date: 2020/10/01
---

# The flights data frame from the nycflights13 package

1. Load and review the data

```{r}
library(tidyverse)
library(nycflights13)
data("flights")
# What are the variables?
names(flights)
# How many observations (rows) are there?
nrow(flights)
# Look at the first three rows
head(flights, n = 3)
```

2. Worst Plane to Fly

```{r}
# Which planes (tailnum) have the three worst (highest) average departure delay record?
flights%>%
  filter(!is.na(dep_delay))%>%
  slice_max(dep_delay, n=3)%>%
  select(tailnum,dep_delay)
# How many flights did it make?
flights%>%
  filter(!is.na(dep_delay))%>%
  slice_max(dep_delay, n=3)%>%
  select(tailnum,flight,dep_delay)
# Now only look tailnums where each flew more than 12 flights and find the three tailnums with the highest average departure delay
flights%>%
  filter(flight > 12)%>%
  filter(!is.na(dep_delay))%>%
  slice_max(dep_delay, n=3)%>%
  select(tailnum)
```

3. Best Time of Day to Fly

```{r}
flights%>%
  group_by(hour)%>%
  summarize(mean_delay = mean(arr_delay, na.rm = TRUE) +
              mean(dep_delay, na.rm = TRUE))%>%
  ggplot(aes(x = as.numeric(hour), y = mean_delay)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  theme_bw() +
  xlab("Hour") +
  ylab("Mean Delay Time")
```

4. Worst Flight Numbers for each Destination

```{r}
flights%>%
  select(dest,arr_delay,tailnum)%>%
  group_by(dest)%>%
  filter(arr_delay > 0)%>%
  mutate(total_arr_delay = sum(arr_delay, na.rm = TRUE),
         pro_arr_delay = arr_delay/total_arr_delay, na.rm = TRUE)
```

5. Destinations with Multiple Carriers from NYC Area

```{r}
flights %>%
  group_by(dest)%>%
  summarise(num_carrier = n_distinct(carrier))%>%
  filter(num_carrier >= 2)%>%
  arrange(desc(num_carrier))%>%
  slice(25:30)
```

6. Effect of the Delay in the Flight before Yours

```{r}
# Using lag() and cor()...
flights%>%
  filter(!is.na(dep_delay))%>%
  mutate(pre_dep_delay = lag(dep_delay,default = 0)) ->
  flights_dep_delay

cor(flights_dep_delay$dep_delay, flights_dep_delay$pre_dep_delay)

# EXTRA CREDIT...
flights_dep_delay%>%
  slice_sample(n = 5000)%>%
  ggplot(aes(x = dep_delay,y = pre_dep_delay)) +
  geom_point()
```

## Star Wars Characters

1. Load the data into R and load any necessary packages

```{r}
library(tidyverse)
data("starwars")
```

2. Use appropriate R code to determine which individuals have missing gender. Make sure to only print out their names and heights, arranged in ascending order of height

```{r}
starwars%>%
  filter(is.na(gender) == TRUE)%>%
  select(name, height)%>%
  arrange(height)
```

3. It seems all individuals in part 2 are droids. Change their gender to "droid" and save to the dataframe

```{r}
starwars$gender[is.na(starwars$gender)] <- "droid"
starwars%>%
  select(name, height, gender)%>%
  filter(gender == "droid")
```

4. BMI

```{r}
# Calculate the BMI and add it to the starwars data frame
starwars%>%
  mutate(bmi = mass / (height/100)^2)%>%
# Sanity check: The median BMI should be in the 20-30 range
  mutate(Sanity_check = case_when(
    bmi>=20 & bmi<=30 ~ "checked"
  ))
```

5. Calculate the median and mean height for each gender as well as the number of individuals

```{r}
starwars%>%
  group_by(gender)%>%
  summarize(mean_height = mean(height, na.rm = TRUE),
            median_height = median(height, na.rm = TRUE),
            number_of_individuals = length(gender))
```

6. Make boxplots of gender vs BMI. Include only masculine, feminine, and droids. Use the black and white theme

```{r}
starwars%>%
  mutate(bmi = mass / (height/100)^2 )%>%
  filter(!is.na(gender))%>%
ggplot(aes(x = gender,y = bmi)) +
geom_boxplot() +
  scale_y_log10() +
  theme_bw() +
  xlab("Gender") +
  ylab("BMI")
```

7. Make scatterplots of height vs mass, faceting by gender

```{r}
starwars%>%
  ggplot(aes(x = mass,y = height)) +
  geom_point() +
  facet_wrap( ~ gender) +
  xlab("Mass") +
  ylab("Height")
```

8. Reproduce the following plot

```{r}
starwars%>%
  filter(birth_year>0 & birth_year<120)%>%
  mutate(gender = na_if(gender, "droid"))%>%
  ggplot(aes(x = birth_year,y = height, col = gender)) +
  geom_point() +
  geom_smooth(se = FALSE, color = "black", linetype = "dashed") +
  theme_bw() +
  xlab("Birth Year") +
  ylab("Height")
```

### The Palmer Penguins Package

1. 

```{r}
library(tidyverse)
library(palmerpenguins)
data("penguins")
head(penguins)
```

2. Bill Ratio

```{r}
penguins%>%
  mutate(fb_ratio=flipper_length_mm/bill_length_mm)
```

3. Using the data frame from 2., eliminate the penguins with an fb_ration of NA and show the highest four penguins of each sex with only the character variables and fb_ratio

```{r}
penguins%>%
  mutate(fb_ratio=flipper_length_mm/bill_length_mm)%>%
  filter(!is.na(fb_ratio))%>%
  select(sex,fb_ratio)%>%
  group_by(sex)%>%
  slice_max(fb_ratio, n=4)
```

4. For each species and sex, calculate the median of the numeric variables

```{r}
penguins%>%
  group_by(species,sex)%>%
  summarize(across(where(is.numeric),
                  ~ median(.x, na.rm = TRUE)))
```

4.1 Then use an appropriate plot to show median bill length vs bill depth by species and sex

```{r}
penguins%>%
  group_by(species,bill_depth_mm,sex)%>%
  summarize(median_bill_length = median(bill_length_mm,na.rm = TRUE)) ->
  sum_penguins

ggplot(data = sum_penguins,
       mapping = aes(x = bill_depth_mm, y = median_bill_length,
                     col = species, linetype = sex))+
  geom_line()+
  theme_bw()+
  xlab("Bill Depth")+
  ylab("Median Bill Length")+
  scale_color_discrete(name = "Species")+
  scale_linetype_discrete(name = "Sex")
```

4.2 Interpret the plot in one sentence: Female penguin tends to have shorter bill Length than male penguin; Chinstrap and Gentoo species tend to have longer bill length than Adelie.

5. How many rows have no missing values?

```{r}
penguins%>%
  filter(across(everything(),
                ~ !is.na(.x)))%>%
  nrow()
```

6. How many unique values are there for each of the columns that end in "_mm" for each sex

```{r}
penguins%>%
  group_by(sex)%>%
  summarize(across(contains("_mm"),
                   ~ length(unique(.x))))
```















