---
title: "hw_6"
author: "Sihyuan Han"
output:
  pdf_document: default
  html_document: default
---

# Identifying Table Keys in the NASA Weather Dataset

```{r}
library(tidyverse)
library(help = "nasaweather")
library("nasaweather")
data(package = "nasaweather")
```

* 1-1 What are the data frames in this data set? atmos, borders, elev, glaciers, storms

* 1-2,3 What are the keys in each data frame?
```{r}
data("atmos")
head(atmos)

atmos %>% 
  group_by(lat,long,year,month) %>% 
  count() %>% 
  filter(n>1)
```

```{r}
data("borders")

borders %>% 
  ungroup() %>% 
  head()

borders %>% 
  ungroup() %>% 
  summarize(dist = nrow(distinct(.)))
nrow(borders)

borders %>% 
  ungroup() %>% 
  distinct(.keep_all = TRUE) %>% 
  group_by(country,long,lat) %>% 
  count() %>% 
  filter(n>1)
```

```{r}
data("elev")
head(elev)

elev %>% 
  group_by(long,lat) %>% 
  count() %>% 
  filter(n>1)
```

```{r}
data("glaciers")
head(glaciers)

glaciers %>% 
  group_by(id) %>% 
  count() %>% 
  filter(n>1)
```

```{r}
data("storms")
head(storms)

storms %>% 
  group_by(name,year,month,day,hour,lat) %>% 
  count() %>% 
  filter(n>1)
```

## Lahman’s Baseball Dataset

```{r}
library(Lahman)
help("Lahman-package")
```

* 2-1
```{r}
data("Master")
data("Batting")
data("Pitching")
data("Fielding")
data("Teams")
data("Salaries")
```

* 2-2
```{r}
# identify primary key
Teams %>% 
  group_by(yearID,teamID) %>% # primary key
  count() %>% 
  filter(n>1)

Master %>% 
  group_by(playerID) %>% # primary key
  count() %>% 
  filter(n>1)

Fielding %>% 
  group_by(playerID,yearID,stint,POS) %>% # primary key
  count() %>% 
  filter(n>1)
```

```{r}
Teams %>% 
  filter(yearID >= 1903) %>% 
  filter(LgWin == "Y") %>% 
  filter(!is.na(WSWin)) %>% # not played each year
  filter(teamID == "BOS") %>% 
  select(yearID,teamID,LgWin) ->
  team_bos_Lgwin

team_bos_Lgwin %>% 
  left_join(Fielding, by = c("yearID","teamID")) %>% 
  left_join(Master, by = "playerID") %>% 
  filter(stint >= 1) %>% 
  select(nameFirst,nameLast,yearID) %>% 
  distinct() %>% 
  arrange(nameLast) %>% 
  head(n=10)
```

* 2-3-a
```{r}
# head(Salaries)
Salaries %>%
  group_by(yearID,playerID) %>%
  summarize(salary_total = sum(salary, na.rm = TRUE)) ->
  Salaries_3_a
Salaries_3_a
```

* 2-3-b
```{r}
Batting %>% 
  left_join(Master, by = "playerID") %>% 
  select(AB,H,playerID,yearID) %>% 
  group_by(yearID,playerID) %>% 
  summarize(sum_bats = sum(AB), sum_hits = sum(H)) ->
  Batting_3_b
Batting_3_b
```

* 2-4-a
```{r}
Batting_3_b %>% 
  left_join(Salaries_3_a, by = c("yearID","playerID")) %>% 
  mutate(bat_avg = sum_hits/sum_bats) %>% 
  filter(sum_bats >= 400) %>% 
  filter(yearID >= 1985) ->
  Batting_4_a
Batting_4_a
```

* 2-4-b hexplot
+ Based on the hexplot, we can see batting average between 0.25-0.3 has lower salary than others. 
```{r}
Batting_4_a %>% 
  ggplot(aes(bat_avg, salary_total))+
  geom_hex()+
  scale_y_log10()
```

* 2-4-c
+ We can learn from the plot(OLS) that the relationship between batting average and salary is positive, so when batting average is high, the salary is high.
```{r}
Batting_4_a %>% 
  ggplot(aes(bat_avg, salary_total))+
  scale_y_log10()+
  geom_smooth(se = FALSE, method = "lm")
```

* 2-4-d
+  The pairwise complete correlation between batting average and log of the total salary by year has negative coefficients. As year pass, the correlation is decreasing. 
```{r}
Batting_4_a %>%
  group_by(yearID) %>% 
  summarize(pc_cor = cor(bat_avg, log(salary_total), use="pairwise")) ->
  Batting_pc_cor
Batting_pc_cor

Batting_pc_cor %>% 
  ggplot(aes(yearID, pc_cor))+
  geom_smooth(se = FALSE, method = "lm")
```

* 2-5
```{r}
head(Master)
Salaries_3_a %>% 
  left_join(Master, by = "playerID") %>% 
  filter(nameFirst == "John") %>% 
  filter(yearID %% 2 == 0) %>% 
  arrange(desc(salary_total), n = 10) %>% 
  select(yearID, nameFirst, nameLast, salary_total)
```

### NYC Flights

* 3-1
```{r}
library(dbplyr)
library(RSQLite,lib.loc = "C:/Users/Stephanie/Documents/R/win-library/4.0")

conn <- dbConnect(drv = SQLite(), dbname = "../R_data/nycflights13.sqlite")
```

* 3-2
```{r}
dbListTables(conn)
```

* 3-3
```{r}
airlines_db <- tbl(conn,"airlines")
airports_db <- tbl(conn,"airports")
flights_db <- tbl(conn,"flights")
planes_db <- tbl(conn,"planes")
weather_db <- tbl(conn,"weather")
```

* 3-4 in-memory data frame, only for flights that actually departed
```{r}
head(airports_db)
head(flights_db)
flights_db %>% 
  collect() ->
  flights

airports_db %>% 
  collect() ->
  airports

flights %>% 
  summarize(across(everything(),~sum(is.na(.))))

flights %>% 
  filter(!is.na(dep_time)) ->
  flights_check_dep
head(flights_check_dep)
```

* 3-5  in-memory data frame, airports served by NYC airports, 104 rows
```{r}
airports %>% 
  semi_join(flights, by = c("faa" = "dest")) ->
  airports_dest

airports %>% 
  semi_join(flights, by = c("faa" = "origin")) ->
  airports_origin

rbind(airports_dest, airports_origin) ->
  airports_by_NYC

airports_by_NYC
```

* 3-6
```{r}
flights_check_dep %>% 
  anti_join(airports_by_NYC, by = c("dest" = "faa")) %>% 
  group_by(dest) %>% 
  summarize(total_flights = n())
```

* 3-7
```{r}
flights_check_dep %>%
  inner_join(airports, by = c("dest" = "faa")) %>% 
  group_by(name,dest) %>% 
  summarize(sum = n()) %>% 
  arrange(desc(sum)) %>% 
  head(n = 10) ->
  flights_dest_top10
flights_dest_top10
```

* 3-8-a
```{r}
head(airlines_db)
airlines_db %>% 
  collect() ->
  airlines

airlines %>% 
  semi_join(flights, by = "carrier") ->
  airlines_nyc
airlines_nyc
```

* 3-8-b
```{r}
flights_dest_top10 %>% 
  left_join(flights, by = "dest") %>% 
  group_by(name, dest, carrier) %>% 
  summarize(median_arr_delay = median(arr_delay, na.rm = TRUE),
            flights = n()) %>% 
  group_by(dest) %>% 
  arrange((median_arr_delay)) %>% 
  slice(1:2) %>% 
  select(-carrier)
```

* 3-8-c
```{r}
flights_dest_top10 %>% 
  left_join(flights, by = "dest") %>% 
  group_by(name, dest, carrier) %>% 
  summarize(median_arr_delay = median(arr_delay, na.rm = TRUE),
            flights = n()) %>% 
  arrange(desc(median_arr_delay)) %>% 
  head(n = 10) %>% 
  select(-carrier)
```

