---
title: "hw_7"
arthor: "Sihyuan Han"
output:
  html_document: default
  pdf_document: default
---

# Scrabble Words

```{r}
library(tidyverse)
library(dplyr)
```


* 1-1 How many words are there?
```{r}
scrabble_w <- read_csv("words.txt")
head(scrabble_w)
scrabble_w[is.na(scrabble_w)] <- "NA"
scrabble_w %>% 
  summarise(across(everything(), ~sum(is.na(.))))
nrow(scrabble_w)
```

* 1-2 How many words either begin or end in “X”?
```{r}
scrabble_w %>% 
  filter(str_detect(word, "^X") | str_detect(word, "X$")) %>% 
  nrow()
```

* 1-3 How many words contain all of the vowels?
```{r}
scrabble_w %>% 
  filter(str_detect(word, "A") & str_detect(word, "E") & str_detect(word, "I") & str_detect(word, "O") & str_detect(word, "U")) ->
  scrabble_w_vowels
  nrow(scrabble_w_vowels)
```

* 1-4 What are the shortest words that contain all of the vowels?
```{r}
scrabble_w_vowels %>% 
  mutate(length = str_length(word)) %>% 
  arrange(length) %>% # shortest is 7 letters
  filter(length == 7)
```

* 1-5 Update the data frame to include a new column of words where you switch the first and last letters of all of the words and a second column to indicate if they are still valid words.
```{r}
scrabble_w %>% 
  mutate(switch_word = str_replace_all(word, "^([A-Z])(.*)([A-z])$", "\\3\\2\\1")) %>% 
  mutate(still_word = switch_word %in% word) ->
  valid_word_check
head(valid_word_check)
```

* 1-6  How many of the words that are still valid words after switching the first and last letters have different first and last letters?
```{r}
valid_word_check %>% 
  filter(still_word == TRUE) ->
  still_word_df # still words

still_word_df %>% 
  filter(str_detect(word, "^(.)(.*)\\1$")) -> # same first and last letter
  same_FL
still_word_df %>% 
  anti_join(same_FL) ->
  diff_FL

head(diff_FL)
nrow(diff_FL)
```

* 1-7 What are the longest words that are still words after switching the first and last letters and where the first and last letters are different?
```{r}
diff_FL %>% 
  mutate(length = str_length(word)) %>% 
  arrange(desc(length)) %>% # longest is 14 letters
  filter(length == 14)
```

* 1-8 Scrabble Scores

* 1-8-a
```{r}
score_word <- function(x){
  low <- c("A","E","I","O","U","D","L","M","N","R","S","T","Y")
  med <- c("B","C","F","G","H","K","P","W", "V")
  high <- c("J","Q","X","Z")
  points <- c(1,4,10)
  sum_score <- (str_count(x, "[AEIOUDLMNRSTY]")*1 + str_count(x, "[BCFGHKPWV]")*4 + str_count(x, "[JQXZ]")*10)
}
scrabble_w %>% 
  mutate(points = score_word(word)) ->
  scrabble_w_scores
head(scrabble_w_scores)
```

* 1-8-b
```{r}
scrabble_w_scores %>% 
  mutate(length = str_length(word)) %>%
  filter(length == 7) %>% 
  slice_max(points, n=2)
```

* 1-8-c
```{r}
# three highest scoring words with no vowels
scrabble_w_scores %>% 
  filter(str_detect(word, "^[^AEIOU]+$")) %>% 
  slice_max(points, n=3)
# three longest scoring words with no vowels
scrabble_w_scores %>% 
  mutate(length = str_length(word)) %>% 
  filter(str_detect(word, "^[^AEIOU]+$")) %>% 
  arrange(desc(length)) %>% 
  slice(1:3)
```

* 1-8-d
```{r}
scrabble_w_scores %>% 
  mutate(vowels_count = str_count(word, "[AEIOU]")) %>% 
  mutate(length = str_length(word)) %>% 
  filter(length <= 7) %>% 
  ggplot(aes(x = as.factor(vowels_count),y = points)) +
  geom_boxplot() +
  xlab("Number of Vowels") +
  ylab("Score") +
  ggtitle("Possible Scores for Seven-Letter Words")
```

* 1-8-f Interpret: As the plot shows that 2-4 vowels in a word has approximately same average of score , which is higher than other words with less or more vowels. 

## Bank Data

* 2-1 show only how many rows there are in the data frame, Show a random sample of 2 percent of the rows.
```{r}
bank_df <- read_csv("../R_data/fed_large_c_bank_ratings.csv")
nrow(bank_df)
bank_df %>% 
  slice_sample(prop = .02)
```

* 2-2 
```{r}
bank_df %>% 
  separate(name,
           into = c("name", "alternate_name"),
           sep = "/",
           extra = "drop") ->
  bank
head(bank)
```

* 2-3 How many bank primary names begin with a digit?
```{r}
bank %>% 
  filter(str_detect(name, "^\\d")) %>% 
  nrow()
```

* 2-4-a  How many of the bank primary names have the letters “BANK” in them? “BANKING” counts
```{r}
bank %>% 
  filter(str_detect(name, "BANK")) %>% 
  nrow()
```

* 2-4-b How many of the bank primary names have the stand-alone word “BANK” in them? “BANKING” does not count
```{r}
bank %>% 
  filter(str_detect(name, "^BANK\\s") | str_detect(name, "\\sBANK\\s") | str_detect(name, "\\sBANK$")) %>% 
  nrow()
```

* 2-5-a
```{r}
bank %>% 
  mutate(name = str_replace_all(name, "BK", "BANK")) ->
  bank_newname
head(bank_newname)
```

* 2-5-b
```{r}
bank_newname %>%
  mutate(position = 
  ifelse(str_detect(name, "^BANK"), "start",
  ifelse(str_detect(name, "BANK$"), "end",
  ifelse(str_detect(name, "\\s(.*)BANK(.*)\\s"), "middle", "none")))) ->
  bank_wposition
head(bank_wposition)
```

* 2-5-c
```{r}
bank_wposition %>% 
  group_by(position) %>% 
  summarise(prop = n()/nrow(bank_wposition))
```

* 2-6 Interpret: The position of the word "BANK" doesn't have significant relationship to the log of total assets.
```{r}
bank_wposition %>% 
  ggplot(aes(x = position, y = consolidated_assets)) +
  geom_boxplot() +
  scale_y_log10()
```


