---
title: "hw_8"
author: "Sihyuan_Han"
output:
  pdf_document: default
  html_document: default
---

# Covid Analysis

* 1-1,2 
```{r}
library(readr)
library(tidyverse)
library(usmap)
library(ggplot2)
us_covid_data <- read_csv("../R_data/us-counties.csv")
us_covid_data %>% 
  saveRDS("../R_output/us-counties.rds")
us_covid <- readRDS("../R_output/us-counties.rds")
```

* 1-3 How many rows of data are there and what is the most recent date?
```{r}
nrow(us_covid)
head(us_covid)
max(us_covid$date)
```

* 1-4
```{r}
read_csv("../R_data/us-counties.csv",
         col_types = cols(
           county = col_factor(),
           state = col_factor()
         )) ->
  c_data
c_data %>% 
  arrange(state, county) ->
  c_data
nlevels(c_data$county)
nlevels(c_data$state)
```

* 1-4-d How many unique combinations of county and state are there?
```{r}
nrow(unique(c_data[,c("county","state")]))
```

* 1-5 Many county names appear in multiple states
```{r}
c_data %>% 
  filter(county != "Unknown") %>% 
  group_by(county) %>% 
  summarise(count = length(unique(state))) %>% 
  arrange(desc(count)) %>% 
  head()
```

* 1-6 Daily cumulative data
```{r}
c_data %>% 
  arrange(state, county, date) %>% 
  group_by(state, county) %>% 
  mutate(first_date = min(date),
         first_case = cases[date == first_date],
         first_death = deaths[date == first_date],
         daily_cases = c(min(first_case),diff(cases)),
         daily_deaths = c(min(first_death),diff(deaths))) %>% 
  select(date, county, state, fips, cases, daily_cases, deaths, daily_deaths) ->
  c_daily_data
head(c_daily_data)
# check Hawaii
c_daily_data %>% 
  filter(county == "Maui") %>% 
  tail(n=10)
```

* 1-7 Create a data frame with the daily totals for cases and deaths by state

+ interpret 1: For the daily cases plot, we can see in the beginning New York has a lot of cases and then they tend to control it. In the middle of the year, Florida and California has lots of cases. And then After FL and CA we can see Texas and Georgia also went high around October, and recently Illinois went up high too. 

+ interpret 2: For the daily deaths plot, NY has the highest death of covid when it first burst out, and then they control it. NJ bursts out lots of death around June and July then Texas occurs more death too after NJ. 
```{r}
c_daily_data %>% 
  group_by(date, state) %>% 
  summarise(daily_c_by_state = sum(daily_cases),
            daily_d_by_state = sum(daily_deaths)) ->
  daily_data_by_state

# Use this to create a line plot with the daily cases color coded by state
daily_data_by_state %>% 
  ggplot(aes(x = date, y = daily_c_by_state)) + 
  geom_line(aes(color = state)) +
  theme(legend.position="remove") +
  geom_text(data = 
              daily_data_by_state %>% 
              filter(daily_c_by_state < -1000 | daily_c_by_state > 10000),
            aes(label = state))

# Use this to create a line plot with the daily deaths color coded by state
daily_data_by_state %>% 
  ggplot(aes(x = date, y = daily_d_by_state)) + 
  geom_line(aes(color = state)) +
  theme(legend.position="remove") +
  geom_text(data = 
              daily_data_by_state %>% 
              filter(daily_d_by_state > 1000),
            aes(label = state))
```

* 1-8 Find the top 5 states and then the top five counties in terms of total deaths
```{r}
# top 5 states
c_daily_data %>% 
  group_by(state) %>% 
  summarise(state_total_death = sum(daily_deaths), 
            record = n()) %>% 
  arrange(desc(state_total_death)) %>% 
  head(n=5)
# top 5 counties
c_daily_data %>% 
  group_by(state, county) %>% 
  summarise(county_total_death = sum(daily_deaths), 
            record = n()) %>% 
  arrange(desc(county_total_death)) %>% 
  head(n=5)
```

* 1-9 DMV Data

+ interpret: As we can see from the plot that around may and June three states are having most cases , especially MD has the highest cases in DMV area at that time. The daily cases starts to go down after the middle of the year and it comes back high recently.  
```{r, warning = FALSE}
c_daily_data %>% 
  filter(state == "Virginia") %>% 
  filter(county != "Frederick") %>% 
  filter(county != "Montgomery") ->
  c_va_df
c_daily_data %>% 
  filter(state == "District of Columbia" | state == "Maryland") %>% 
  rbind(c_va_df) -> define_dmv_data
define_dmv_data %>% 
  filter(county == c("Anne Arundel", "Charles", "Frederick", "Howard", "Montgomery", "Prince George's", "Alexandria city", "Arlington", "Fairfax city", "Fairfax", "Loudoun", "Manassas", "Manassas city", "Manassas Park city", "Prince William", "District of Columbia")) -> full_df_dmv 

full_df_dmv %>% 
  group_by(date, county, state) %>% 
  summarise(county_total_cases = sum(daily_cases),
            county_total_deaths = sum(daily_deaths)) ->
  df_dmv
 
df_dmv %>% 
  ggplot(aes(x = date, y = county_total_cases)) +
  geom_line() +
  scale_y_log10() +
  facet_wrap( ~state)
```

# Maps

* 2-1 Load the usmap package
```{r}
library(usmap)
```

* 2-2 Use a tidyverse function to create a variable with the FIPS codes for the DMV

```{r}
full_df_dmv %>% 
  select(county, fips) %>% 
  unique() -> df_dmv_fips

as.numeric(df_dmv_fips$fips) -> dmv_fips
dmv_fips
```

* 2-3 Plot the counties along with their names and a title
```{r}
plot_usmap(regions = "counties", include = dmv_fips, labels = TRUE) + 
  labs(title = "DMV counties") +
  theme(panel.background = element_rect(color = "blue", fill = "lightblue"))
```

* 2-4 Plot the maximum of the daily case count and death count for the DMV areas

+ interpret 1: In the "Maximum Daily Cases as of 11/13", we can see Prince George's in Maryland has the highest cases in DMV area, following with Montgomery MD and Fairfax VA. 

+ interpret 2: In the "Maximum Daily Deaths as of 11/13", we can see Prince George's and Montgomery in Maryland has the highest deaths in DMV area, following with Fairfax VA, which is reasonable since the cases in these three counties are also the highest. 
```{r}
full_df_dmv %>% 
  group_by(date, state, county, fips) %>% 
  summarise(max_daily_case = max(cases),
            max_daily_death = max(deaths)) ->
  dmv_county_plot

# Plot the maximum of the daily case count for the DMV areas
plot_usmap(data = dmv_county_plot, include = dmv_fips, values = "max_daily_case", color = "blue") +
  scale_fill_continuous(low = "white", high = "red",
                        name = "cases", label = scales::comma) +
  labs(title = "DMV Region",
       subtitle = paste0("Maximum Daily Cases as of ", 
                         max(dmv_county_plot$date))) + 
  theme(panel.background = element_rect(color = "black", fill = "white")) +
  theme(legend.position = "top")

# Plot the maximum of the daily death count for the DMV areas
plot_usmap(data = dmv_county_plot, include = dmv_fips, values = "max_daily_death", color = "blue") +
  scale_fill_continuous(low = "white", high = "red",
                        name = "cases", label = scales::comma) +
  labs(title = "DMV Region",
       subtitle = paste0("Maximum Daily Deaths as of ", 
                         max(dmv_county_plot$date))) + 
  theme(panel.background = element_rect(color = "black", fill = "white")) +
  theme(legend.position = "top")
```

