---
title: "hw_9"
author: "Sihyuan_Han"
output:
  pdf_document: default
  html_document: default
---

# Capital Bikeshare Data

* 1-1 Use a readr function to load in the trips data and the station data from the data folder
```{r}
Sys.setlocale("LC_TIME","English")
library(readr)
library(tidyverse)
library(lubridate)
capital_trips_2016_df <- read_csv("../R_data/capital_trips_2016.csv")
capital_stations <- read_csv("../R_data/capital_stations.csv")
```

```{r}
# Review and rename variables that have spaces in the names
# glimpse(capital_trips_2016_df)
capital_trips_2016_df %>% 
  rename(Duration_ms = `Duration (ms)`,
         Start_date = `Start date`,
         End_date = `End date`,
         Start_station_number = `Start station number`,
         Start_station = `Start station`,
         End_station_number = `End station number`,
         End_station = `End station`,
         Bike_number = `Bike number`,
         Member_Type = `Member Type`) -> 
  capital_trips_2016
glimpse(capital_trips_2016)
glimpse(capital_stations)
```

* 1-2 Use lubridate functions to convert the date-time information in the trip data to a date time variable
```{r}
capital_trips_2016 %>% 
  mutate(Start_date = force_tz(mdy_hm(Start_date), tzone = "America/New_York"),
         End_date = force_tz(mdy_hm(End_date), tzone = "America/New_York")) ->
  capital_trips_2016
glimpse(capital_trips_2016)
```

* 1-3 Calculate the average number of trips for each weekday, given the day has trips. There are several days with no trips
```{r}
capital_trips_2016 %>% 
  separate(Start_date, into = c("Start_date", "Start_time"), sep = " ") %>%
  group_by(Start_date)%>%
  summarise(total_trips = n()) %>%
  mutate(wday = wday(Start_date, label = TRUE)) %>%
  group_by(wday) %>%
  summarise(mean_num_trips = mean(total_trips)) ->
  sumdf
glimpse(sumdf)
```

* 1-4 Reproduce this plot in R
```{r}
sumdf %>% 
  ggplot(aes(x = fct_rev(wday), y = mean_num_trips)) +
  geom_point() +
  theme_bw() +
  xlab("Weekday") +
  ylab("Mean Number of Trips")
```

* 1-5 In a stunning show of contempt, the IEEE Computer Society decided to add a new weekday called “Fooday” with abbreviation “Foo”
```{r}
Fooday_df <- tribble(~wday, ~mean_num_trips, 
                  "Foo", 12567)
wday_abb <- c("Foo","Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat" )
bind_rows(Fooday_df, sumdf) %>% 
  mutate(wday = parse_factor(wday, levels = wday_abb)) %>% 
  mutate(mean_num_trips = round(mean_num_trips)) -> 
  sumdf_w_foo
sumdf_w_foo
```

* 1-6 In another stunning show of contempt, the IEEE Computer Society decided to change the abbreviations from three letters to two letters
```{r}
sumdf_w_foo %>% 
  mutate(wday = fct_recode(wday,
                           "Fo" = "Foo",
                           "Su" = "Sun",
                           "Mo" = "Mon",
                           "Tu" = "Tue",
                           "We" = "Wed",
                           "Th" = "Thu",
                           "Fr" = "Fri",
                           "Sa" = "Sat")) ->
  sumdf_shortabb
sumdf_shortabb
```

* 1-7 
```{r}
capital_stations %>% 
  mutate(start_time = ymd_hms("1970-01-01 00:00:00", tz = "America/New_York"),
         installDate = start_time + dmilliseconds(installDate)) %>% 
  ggplot(aes(x = installDate)) +
  geom_histogram() +
  xlab("Install Date") +
  ylab("Count") +
  theme_bw()
```

## Reddit Data

* 2-1 Use a readr function to read in the data from the all_comments.csv in the data folder
```{r}
all_comments_df <- read_csv("../R_data/all_comments.csv")
glimpse(all_comments_df)
```

* 2-2 Use a lubridate function to convert the character dates into date variables so there are no parsing errors
```{r}
all_comments_df %>% 
  mutate(post_date = dmy(post_date),
         comm_date = dmy(comm_date),
         subreddit = as.factor(subreddit)) -> 
  all_comments
glimpse(all_comments)
```

* 1-3 Compute the difference between the post date and the comment date as a period and remove all records where the difference is 0 and save the data frame
```{r}
all_comments %>% 
  mutate(period = as.duration(comm_date-post_date)) %>% 
  filter(period != 0) -> 
  all_comments_new
glimpse(all_comments_new)
```

* 1-4 Reproduce the following plot
```{r}
all_comments_new %>% 
  group_by(subreddit, period) %>% 
  summarise(median_num_com = median(num_comments)) %>% 
  mutate(subreddit = fct_reorder(subreddit, median_num_com)) %>% 
  mutate(subreddit = fct_relevel(subreddit, "anaesthesia",
                                 after = length(levels(all_comments_new$subreddit))-1)) %>% 
  mutate(subreddit = fct_relevel(subreddit, "COVID19",
                                 after = length(levels(all_comments_new$subreddit))-3)) %>% 
  ggplot(aes(x = period, y = median_num_com, color = subreddit)) +
  scale_y_log10() +
  geom_point() +
  geom_smooth(se = F, method = "lm") +
  xlab("Time After Posting of Comments") +
  ylab("Medain Number of Comments") +
  ggtitle("Comments by Subreddit Over Time")
```


